Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle structure

### 2017-06-01 documents/TriangleScenarioArXiv/ts.tex
removed appendix A1
added review section for Bell structure

    From a foundational prospective, the most robust demonstrations of quantum phenomena with no classical emulation have involved Bell inequalities~\cite{Bell_1964}. Originally, Bell inequalities were derived as a way to show that no hidden variable theory could ever account for quantum mechanics; in this sense Bell inequalities are a response to the famous EPR paradox~\cite{EPR_Orig}. The enumeration of Bell inequalities has since become a widespread systematic way of demonstration the \textit{non-classicality} of a given observation. More recently it has been appreciated that Bell inequalities can understood as consequences of \term{causal inference}~\cite{Wood_2012}. Causal inference is concerned with classifying observations into those which can and cannot be explained by a hypothesized causal structure. The abstract nature of causal inference is responsible for its presence in numerous scientific fields including machine learning and biology~\cite{Pearl_2009,Pearl_2009_tr}. Causal compatibility inequalities, such as Bell and Instrumental inequalities, characterize the space of observations that are compatible with a hypothesized causal structure, albeit the characterization offered by practically derivable inequalities is often only an approximation. To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell structure, as depicted in \cref{fig:bell_scenario}. The fundamental Bell structure involves non-communicating parties making measurements on some hidden shared resource $\la$, where the measurement outcomes ($A, B$) are presumed to be stochastic functions of the the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$. Quantum non-classicality in the Bell structure has been thoroughly studied since Bell's original work~\cite{Brunner_2013}. More complex structures, however, such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014}, are much less understood. Here we investigate one particular causal structure: the Triangle structure (\cref{fig:triangle_structure}).

@@

    % A number of causal structures are depicted throughout this document (see \cref{fig:bell_scenario,fig:triangle_structure,fig:inflations}). As an example, the Triangle structure has $3$ observable nodes and $3$ latent nodes,
    % \[ \nodes_{O} = \bc{A, B, C} \qquad \nodes_{L} = \bc{X, Y, Z} \]
    % along with $6$ edges indicating that the latent nodes $\bc{X, Y, Z}$ cause and influence the observed nodes $\bc{A, B, C}$.
    % \[ \edges = \bc{\bc{X \to A}, \bc{Y \to A}, \bc{Y \to B}, \bc{Z \to B}, \bc{Z \to C}, \bc{X \to C}} \]

@@

    There are several approaches to tackling the compatibility problem when dealing with latent variables; there are two naive approaches worth mentioning here. The first is to recognize that the conditional independence constraints implied by d-separation relations over the \textit{observable} variables form a family of necessary constraints for $\prob[\nodes_{O}]$. The failure to satisfy one of these observable independence relations immediately qualifies $\prob[\nodes_{O}]$ as incompatible with $\graph$. Often, the observable d-separation relations implied by a causal structure form an \textit{insufficient} set of constraints for compatible distributions. Such causal structures have been termed \textit{interesting}~\cite{Henson_2014}, and more involved classification techniques must be used~\cite{Inflation}. The principle focus of this paper is the Triangle structure and has been shown to be one of the smallest interesting causal structures~\cite{Henson_2014}. An alternative approach requires the cardinality (number of outcomes) of the latent variables to be fixed. In most realistic scenarios, the nature of the latent variables is completely unspecified. More powerful approaches find constraints for $\prob[\nodes]$ in the form of probabilistic inequalities defined over $\prob[\nodes_{O}]$ and its marginals which constraint the set of compatible probability distributions. We term these constraints \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of simply Bell inequalities for two reasons. Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure. Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.} If a probability distribution $\prob[\nodes_{O}]$ happens to \textit{violate} any causal compatibility inequality, then that distribution deemed \textit{incompatible}. In \cref{sec:deriving_inequalities}, a brief discussion of existing techniques for deriving these inequalities will take place.

@@

    \section{Bell Structure}
    \label{sec:bell_structure}
    \todo[TC]{Review of Bell structure, Tsirelson-box, CHSH inequality}

    \[ \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 0} + \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 1} + \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 0} - \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 1} \leq 2 \eq \label{eq:CHSH_ineq_orig} \]

    \begin{figure}
    \begin{center}
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
            \caption{The Bell structure consisting of two observers $\p{A}, \p{B}$ together with measurement settings $S_{\p{A}}$ and $S_{\p{B}}$ respectively. The shared hidden variable is labeled $\la$.}
            \label{fig:bell_scenario}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure}}
            \caption{The casual structure of the Triangle structure. Three variables $A,B,C$ are observable, while $X, Y, Z$ are latent variables.}
            \label{fig:triangle_structure}
        \end{minipage}
    \end{center}
    \end{figure}
    \section{Triangle structure}
    \label{sec:triangle_structure}

    Discovering quantum non-classicality in any causal structure is desirable, so why, in particular, is it important to do so in the Triangle structure? As was mentioned in \cref{sec:introduction,sec:causal_compatibility}, the \term{Triangle structure} (\cref{fig:triangle_structure}) is a causal structure $\graph$ consisting of $3$ observable variables $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$. Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the Triangle structure if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that
    %the joint distribution $\prob[\nodes] = \prob[ABCXYZ]$ is a product over the causal parameters,
    %\[ \prob[ABCXYZ] = \prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
    %And also, the given distribution
    $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$:
    \[ \prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \eq \label{eq:triangle_compatibility} \]

@@

    \section{Fritz Distribution}
    \label{sec:fritz_distribution}
    \begin{figure}
    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational_fritz_bell}}
        \caption{The Triangle structure re-imagined to mimic the Bell structure. The measurement settings $S_{\p{A}},S_{\p{B}}$ are latent nodes unlike the Bell structure (\cref{fig:bell_scenario}).}
        \label{fig:triangle_structure_with_fritz_bell_embedded}
    \end{center}
    \end{figure}

    As was originally noticed by \citet{Fritz_2012}, it is possible to construct quantum distributions incompatible with the Triangle structure by utilizing quantum distributions incompatible with the familiar Bell structure. To explain, imagine rearranging the triangle into the configuration depicted in \cref{fig:triangle_structure_with_fritz_bell_embedded} and contrast it with the Bell structure of \cref{fig:bell_scenario}. Evidently, under the correct relabeling, large portions of the Triangle structure resemble the Bell structure. The crucial distinction is that the measurement settings $S_{\p{A}}, S_{\p{B}}$ are \textit{observable variables} in the Bell structure but become \textit{latent variables} in the Triangle structure. In order to embed distributions that are incompatible with the Bell structure into the Triangle structure, the latent nodes $S_{\p{A}}, S_{\p{B}}$ need to be observable and independent of the shared latent node $\la$. This can be accomplished by having $C$ ``measure'' the measurement settings $S_{\p{A}}, S_{\p{B}}$ and announce them as an outcome. Consequently, any distribution over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ that is incompatible with Bell structure is also incompatible with the Triangle structure provided that $C$ is \textit{perfectly correlated} with $S_{\p{A}}, S_{\p{B}}$~\cite{Fritz_2012}. Understandably there are numerous ways that this can be accomplished, albeit we will focus on elucidating an exemplary method.

@@

    Here the notation $\prob[\fritz][abc] = \prob[\p{ABC}][abc] = \prob[][\p A\mapsto a,\p B\mapsto b,\p C\mapsto c]$ is used as shorthand. The Fritz distribution is quantum-accessible in the sense that $\prob[\fritz]$ can be implemented using a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ realized on \cref{fig:triangle_structure} using \cref{eq:quantum_model_triangle}~\cite{Fritz_2012}. The Fritz distribution is best visualized as a $4 \times 4 \times 4$ grid of possible outcomes as depicted in \cref{fig:fritz_distribution_visualized}. From this diagram, it can be seen that each of $\p{C}$'s outcomes restricts the possible outcomes for $\p A,\p B$ into a $2 \times 2$ block. If one writes the outcome labels $\bc{0,1,2,3}$ in binary $\bc{00,01,10,11}$, it can be seen that the left-hand bits for $\p A$ and $\p B$ (respectively denoted $\p A_l$, $\p B_l$) are fixed by the outcome of $\p C$. Pursuant to the embedding of~\cref{fig:triangle_structure_with_fritz_bell_embedded} the left-hand bits emulate the measurement settings $S_{\p A}$ and $S_{\p B}$ and the right-hand bits emulate a two-outcome measurement performed by $A, B$ as they would in~\cref{fig:bell_scenario}. Specifically, $\p C$'s bits are perfectly correlated with the left-bits of $A,B$; $\p C_l = \p A_l$ and $\p C_r = \p B_l$.

@@

    Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_scenario}) into the Triangle structure via the re-imagined version of the Triangle scenario (\cref{fig:triangle_structure_with_fritz_bell_embedded}). Furthermore, the logic of \cref{sec:fritz_distribution} shows that \textit{any} Bell structure compatibility inequality can be upgraded to a compatibility inequality for the Triangle structure, provided one restricts the domain of those inequalities to distributions possessing appropriate perfect correlations. Suppose one relaxed that restriction, then it becomes qualitatively reasonable to associate incompatibility via violations of upgraded inequalities with the same variety of incompatibility that is familiar in the Bell structure. Therefore, satisfying all such upgraded inequalities is a sufficient condition for a new type of incompatibility that is genuinely distinct from Bell structure incompatibility. Ultimately, it remains unclear whether or not a positive resolution to \ref{r:3} is even feasible.

@@

    \subsection{Satisfaction of d-Separation Relations}
    \label{sec:satisfaction_of_d_sep_relations}
    \todo[TC]{Absorb the relevant components of the next section into this one}
    \todo[TC]{Given a distribution and a causal structure, does the distribution satisfy the conditional d-Separation relations?}

@@

    Each of the above mentioned techniques suffers from computational complexity limitations. For example, the Fourier-Motzkin procedure is in the worst case doubly exponential in the number of initial inequalities~\cite{Dantzig_1973}. For the purposes of this research, solving the marginal problem without reference to a marginal model was intractable. This will become apparent in \cref{sec:exemplary_inflations_of_the_triangle structure} when the Inflation Technique is applied to the Triangle structure, producing marginal models that are very large. Luckily, the Fritz distribution (\cref{sec:fritz_distribution}) allows one to avoid the complexity issues of the complete marginal problem and instead focus on the original problem of determining whether or not a particular marginal model admits a joint distribution or not.
    \subsection{Inflation Technique}
    \label{sec:deriving_inequalities}
    \label{sec:inflation_technique_main_summary}
    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if probability distribution $\prob[\nodes_{O}]$ is compatible or incompatible with a given causal structure $\graph$. As a preliminary summary, the Inflation Technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure. As a example, four inflations of the Triangle structure are depicted in \cref{fig:inflations}. Copies of nodes in the inflated causal structure are distinguished by an additional subscript called the \term{copy-index}. For example, node $A$ of \cref{fig:triangle_structure} has copies $A_1, A_2, A_3, A_4$ in the inflated causal structure in \cref{fig:the_web_inflation}. All such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'. A copy-index is effectively arbitrary, so we will refer to an arbitrary inflated copy of $A$ as $A'$.
    \[ A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B' \]
    We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if and only if $X = Y$ upon removal of the copy-index. In addition to the common graph-theoretic terminology and notation presented in \cref{sec:causal_compatibility}, we define two more concepts necessary to formally define an inflation of $\graph$. First, an \term{induced subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is another graph composed of nodes $N$ and all edges $e$ of the original graph that are contained in $N$: $\Sub[\graph]{N} \defined \br{N, \bc{e = \bc{n \to m} \mid n, m \in N}}$. An \term{ancestral subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$: $\AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}}$.

>>>>

    From a foundational prospective, the most robust demonstrations of quantum phenomena with no classical emulation have involved Bell inequalities~\cite{Bell_1964}. Originally, Bell inequalities were derived as a way to show that no hidden variable theory could ever account for quantum mechanics; in this sense Bell inequalities are a response to the famous EPR paradox~\cite{EPR_Orig}. The enumeration of Bell inequalities has since become a widespread systematic way of demonstration the \textit{non-classicality} of a given observation. More recently it has been appreciated that Bell inequalities can understood as consequences of \term{causal inference}~\cite{Wood_2012}. Causal inference is concerned with classifying observations into those which can and cannot be explained by a hypothesized causal structure. The abstract nature of causal inference is responsible for its presence in numerous scientific fields including machine learning and biology~\cite{Pearl_2009,Pearl_2009_tr}. Causal compatibility inequalities, such as Bell and Instrumental inequalities, characterize the space of observations that are compatible with a hypothesized causal structure, albeit the characterization offered by practically derivable inequalities is often only an approximation. To derive the traditional Bell inequalities from causal inference one starts with a (classical) causal structure known as the Bell structure, as depicted in \cref{fig:bell_structure}. The fundamental Bell structure involves non-communicating parties making measurements on some hidden shared resource $\la$, where the measurement outcomes ($A, B$) are presumed to be stochastic functions of the the local choices of measurement settings ($S_A, S_B$) and the shared resource $\la$. Quantum non-classicality in the Bell structure has been thoroughly studied since Bell's original work~\cite{Brunner_2013}. More complex structures, however, such as the correlation scenarios proposed by Fritz~\cite{Fritz_2012,Fritz_2014}, are much less understood. Here we investigate one particular causal structure: the Triangle structure (\cref{fig:triangle_structure}).

@@

    % A number of causal structures are depicted throughout this document (see \cref{fig:bell_structure,fig:triangle_structure,fig:inflations}). As an example, the Triangle structure has $3$ observable nodes and $3$ latent nodes,
    % \[ \nodes_{O} = \bc{A, B, C} \qquad \nodes_{L} = \bc{X, Y, Z} \]
    % along with $6$ edges indicating that the latent nodes $\bc{X, Y, Z}$ cause and influence the observed nodes $\bc{A, B, C}$.
    % \[ \edges = \bc{\bc{X \to A}, \bc{Y \to A}, \bc{Y \to B}, \bc{Z \to B}, \bc{Z \to C}, \bc{X \to C}} \]

@@

    There are several approaches to tackling the compatibility problem when dealing with latent variables; there are two naive approaches worth mentioning here. The first is to recognize that the conditional independence constraints implied by d-separation relations over the \textit{observable} variables form a family of necessary constraints for $\prob[\nodes_{O}]$. The failure to satisfy one of these observable independence relations immediately qualifies $\prob[\nodes_{O}]$ as incompatible with $\graph$. Often, the observable d-separation relations implied by a causal structure form an \textit{insufficient} set of constraints for compatible distributions. Such causal structures, which include the Bell structure, have been termed \textit{interesting}~\cite{Henson_2014}, and more involved classification techniques must be used~\cite{Inflation}. The principle focus of this paper is the Triangle structure and has been shown to be one of the smallest interesting causal structures~\cite{Henson_2014}. An alternative approach requires the cardinality (number of outcomes) of the latent variables to be fixed. In most realistic scenarios, the nature of the latent variables is completely unspecified. More powerful approaches find constraints for $\prob[\nodes]$ in the form of probabilistic inequalities defined over $\prob[\nodes_{O}]$ and its marginals which constraint the set of compatible probability distributions. We term these constraints \term{causal compatibility inequalities}\footnote{We refer to these inequalities as ``causal compatibility inequalities'' instead of simply Bell inequalities for two reasons. Firstly, ``Bell inequalities'' usually are associated specifically with the Bell structure. Secondly, the inequalities derived in this work are fundamentally distinct from a typical Bell inequality in that these inequalities are \textit{polynomial} over $\prob[\nodes_{O}]$ instead of \textit{linear}.} If a probability distribution $\prob[\nodes_{O}]$ happens to \textit{violate} any causal compatibility inequality, then that distribution deemed \textit{incompatible}. In \cref{sec:deriving_inequalities}, a brief discussion of existing techniques for deriving these inequalities will take place.

@@

    \section{Bell Structure}
    \label{sec:bell_structure}
    This section aims to define the Bell structure and summarize the main results associated with its non-classical character. The purpose of this section is to equip an unfamiliar reader with the pertinent background and also to establish a context for which to draw comparisons between the advancements made toward understanding non-classicality of the Bell structure and the analogous results obtained for Triangle structure in the remainder of this work. Readers familiar with the Bell structure (sometimes called Bell scenario/experiment) will experience little obstacles proceeding to \Cref{sec:triangle_structure}.

    The Bell structure (\cref{fig:bell_structure}) refers to an iconic causal structure involving two distant observers which make local measurements $A, B$ determined by measurement settings $S_A, S_B$ on a shared latent resource $\la$~\cite{Brunner_2013}. The resulting observed correlations form a conditional probability distribution $\prob[AB|S_AS_B]$. Subject to the notions of compatibility presented in \cref{sec:causal_compatibility}, this distribution is compatible with \cref{fig:bell_structure} if and only if there exists some functional specification of $\la$ such that there exists a distribution $\prob[AB|S_AS_B,\la]$ such that $\prob[AB|S_AS_B] = \sum_{\la} \prob[AB|S_AS_B,\la]$ and also satisfies the following implementation of \cref{eq:compatibility_as_factorization}:
    \[ \prob[AB|S_AS_B,\la] = \prob[A|S_A,\la]\prob[B|S_B,\la] \]
    Any observed distribution $\prob[AB|S_AS_B]$ which fails to be explained by the classical causal hypothesis of the Bell structure is appropriately termed non-classical. Often, distributions incompatible with the Bell structure are referred to as non-local because the Bell structure indicates that the latent resource is shared locally and measurements are made locally. In particular,~\citet{Bell_1964} demonstrated that there exists distributions that are non-classical yet are attainable via quantum resources and measurements. If one does not wish to accept fine-tuning arguments, one must accept that quantum correlations can be non-local as no variation to the latent nodes can explain the same correlations~\cite{Wood_2012}.\footnote{This is unlike the Triangle structure wherein a global yet latent common cause is always an acceptable explanation for any correlation and does require fine-tuning. Therefore, we never refer to non-classical correlations in Triangle Structure as non-local.} A distribution is accessible with quantum resources and measurements if there exists a bipartite quantum state $\rho_{AB}$ of arbitrary dimension and measurement operators $M_{A|S_A}, M_{B|S_B}$ conditional indexed by the measurement settings such that $\prob[AB|S_AS_B] = \Tr\bs{\rho_{AB}M_{A|S_A}\otimes M_{B|S_B}}$. The non-classicality of quantum distributions for the Bell structure can be demonstrated through the use of Bell inequalities such as the CHSH inequality (\cref{eq:CHSH_ineq_orig}) which constrain the correlations between binary variables $A$ and $B$ for classical distributions~\cite{CHSH_Original}.
    \[ \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 0} + \ba{\p A\p B | S_{\p{A}} = 0, S_{\p{B}} = 1} + \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 0} - \ba{\p A\p B | S_{\p{A}} = 1, S_{\p{B}} = 1} \leq 2 \eq \label{eq:CHSH_ineq_orig} \]
    Non-trivial Bell inequalities such as the CHSH inequality are capable of distinguishing the non-classical nature of distributions beyond the constraints implied by observable d-separation relations; the inequalities presented in \cref{sec:found_inequalities} are also of this type.

    Finally, must like any causal structure, Bell inequalities act as a measure of the non-classical character of a given distribution. In particular, the antecedent of \cref{eq:CHSH_ineq_orig} has a classical upper-bound of $2$ and it can be shown to have a quantum upper-bound of $2\sqrt{2}$~\cite{Cirelson_1980}. Furthermore, non-classical distributions that are also non-quantum such as the PR-box correlations are upper-bounded by $4$~\cite{PR_1995}. In \cref{sec:found_inequalities}, newly discovered and analogous inequalities for the Triangle structure are presented. Although their associated quantum and post-quantum upper-bounds are currently unknown, an attempt to numerical compute these is discussed in \cref{sec:optimizations}.

    \begin{figure}
    \begin{center}
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
            \caption{The Bell structure consisting of two observers $\p{A}, \p{B}$ together with measurement settings $S_{\p{A}}$ and $S_{\p{B}}$ respectively. The shared hidden variable is labeled $\la$.}
            \label{fig:bell_structure}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure}}
            \caption{The casual structure of the Triangle structure. Three variables $A,B,C$ are observable, while $X, Y, Z$ are latent variables.}
            \label{fig:triangle_structure}
        \end{minipage}
    \end{center}
    \end{figure}
    \section{Triangle structure}
    \label{sec:triangle_structure}

    Discovering quantum non-classicality in any causal structure is desirable, so why, in particular, is it important to do so in the Triangle structure? As was mentioned in \cref{sec:introduction,sec:causal_compatibility}, the \term{Triangle structure} (\cref{fig:triangle_structure}) is a causal structure $\graph$ consisting of $3$ observable variables $A, B, C$ arranged in a triangular configuration while pair-wise sharing latent variables $X, Y, Z$. Following the definition of causal compatibility from \cref{sec:causal_compatibility}, a distribution $\prob[\nodes_{O}] = \prob[ABC]$ is compatible with the Triangle structure if and only if there exists a choice of causal parameters $\bc{\prob[A|X,Y],\prob[B|Y,Z],\prob[C|Z,X],\prob[X],\prob[Y],\prob[Z]}$ such that
    %the joint distribution $\prob[\nodes] = \prob[ABCXYZ]$ is a product over the causal parameters,
    %\[ \prob[ABCXYZ] = \prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \]
    %And also, the given distribution
    $\prob[ABC]$ is a marginalization of $\prob[ABCXYZ]$ over $X, Y, Z$\footnote{Here the summation $\sum$ is used to denote a statistical marginalization over the latent variables $X,Y,Z$ with unspecified support.}:
    \[ \prob[ABC] = \sum_{X,Y,Z}\prob[A|X,Y]\prob[B|Y,Z]\prob[C|Z,X]\prob[X]\prob[Y]\prob[Z] \eq \label{eq:triangle_compatibility} \]

@@

    \section{Fritz Distribution}
    \label{sec:fritz_distribution}
    \begin{figure}
    \begin{center}
        \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure_operational_fritz_bell}}
        \caption{The Triangle structure re-imagined to mimic the Bell structure. The measurement settings $S_{\p{A}},S_{\p{B}}$ are latent nodes unlike the Bell structure (\cref{fig:bell_structure}).}
        \label{fig:triangle_structure_with_fritz_bell_embedded}
    \end{center}
    \end{figure}

    As was originally noticed by \citet{Fritz_2012}, it is possible to construct quantum distributions incompatible with the Triangle structure by utilizing quantum distributions incompatible with the familiar Bell structure. To explain, imagine rearranging the triangle into the configuration depicted in \cref{fig:triangle_structure_with_fritz_bell_embedded} and contrast it with the Bell structure of \cref{fig:bell_structure}. Evidently, under the correct relabeling, large portions of the Triangle structure resemble the Bell structure. The crucial distinction is that the measurement settings $S_{\p{A}}, S_{\p{B}}$ are \textit{observable variables} in the Bell structure but become \textit{latent variables} in the Triangle structure. In order to embed distributions that are incompatible with the Bell structure into the Triangle structure, the latent nodes $S_{\p{A}}, S_{\p{B}}$ need to be observable and independent of the shared latent node $\la$. This can be accomplished by having $C$ ``measure'' the measurement settings $S_{\p{A}}, S_{\p{B}}$ and announce them as an outcome. Consequently, any distribution over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ that is incompatible with Bell structure is also incompatible with the Triangle structure provided that $C$ is \textit{perfectly correlated} with $S_{\p{A}}, S_{\p{B}}$~\cite{Fritz_2012}. Understandably there are numerous ways that this can be accomplished, albeit we will focus on elucidating an exemplary method.

@@

    Here the notation $\prob[\fritz][abc] = \prob[\p{ABC}][abc] = \prob[][\p A\mapsto a,\p B\mapsto b,\p C\mapsto c]$ is used as shorthand. The Fritz distribution is quantum-accessible in the sense that $\prob[\fritz]$ can be implemented using a set of quantum states $\rho_{AB}, \rho_{BC}, \rho_{CA}$ and measurements $M_A, M_B, M_C$ realized on \cref{fig:triangle_structure} using \cref{eq:quantum_model_triangle}~\cite{Fritz_2012}. The Fritz distribution is best visualized as a $4 \times 4 \times 4$ grid of possible outcomes as depicted in \cref{fig:fritz_distribution_visualized}. From this diagram, it can be seen that each of $\p{C}$'s outcomes restricts the possible outcomes for $\p A,\p B$ into a $2 \times 2$ block. If one writes the outcome labels $\bc{0,1,2,3}$ in binary $\bc{00,01,10,11}$, it can be seen that the left-hand bits for $\p A$ and $\p B$ (respectively denoted $\p A_l$, $\p B_l$) are fixed by the outcome of $\p C$. Pursuant to the embedding of~\cref{fig:triangle_structure_with_fritz_bell_embedded} the left-hand bits emulate the measurement settings $S_{\p A}$ and $S_{\p B}$ and the right-hand bits emulate a two-outcome measurement performed by $A, B$ as they would in~\cref{fig:bell_structure}. Specifically, $\p C$'s bits are perfectly correlated with the left-bits of $A,B$; $\p C_l = \p A_l$ and $\p C_r = \p B_l$.

@@

    Moreover \ref{r:3} is justified as a valid interpretation of Fritz's Problem in the following sense: the Fritz distribution was constructed by embedding a quantum distribution incompatible with the Bell structure (\cref{fig:bell_structure}) into the Triangle structure via the re-imagined version of the Triangle scenario (\cref{fig:triangle_structure_with_fritz_bell_embedded}). Furthermore, the logic of \cref{sec:fritz_distribution} shows that \textit{any} Bell structure compatibility inequality can be upgraded to a compatibility inequality for the Triangle structure, provided one restricts the domain of those inequalities to distributions possessing appropriate perfect correlations. Suppose one relaxed that restriction, then it becomes qualitatively reasonable to associate incompatibility via violations of upgraded inequalities with the same variety of incompatibility that is familiar in the Bell structure. Therefore, satisfying all such upgraded inequalities is a sufficient condition for a new type of incompatibility that is genuinely distinct from Bell structure incompatibility. Ultimately, it remains unclear whether or not a positive resolution to \ref{r:3} is even feasible.

@@

    % \subsection{Satisfaction of d-SSeparation Relations}
    % \label{sec:satisfaction_of_d_sep_relations}
    % \todo[TC]{Absorb the relevant components of the next section into this one}
    % \todo[TC]{Given a distribution and a causal structure, does the distribution satisfy the conditional d-Separation relations?}

@@

    Each of the above mentioned techniques suffers from computational complexity limitations. For example, the Fourier-Motzkin procedure is in the worst case doubly exponential in the number of initial inequalities~\cite{Dantzig_1973}. For the purposes of this research, solving the marginal problem without reference to a marginal model was intractable. This will become apparent in \cref{sec:exemplary_inflations_of_the_triangle structure} when the Inflation Technique is applied to the Triangle structure, producing marginal models that are very large. Luckily, the Fritz distribution (\cref{sec:fritz_distribution}) allows one to avoid the complexity issues of the complete marginal problem and instead focus on the original problem of determining whether or not a particular marginal model admits a joint distribution or not.
    \subsection{Inflation Technique}
    \label{sec:deriving_inequalities}
    \label{sec:inflation_technique_main_summary}
    The \term{Inflation Technique}, invented by \citet{Inflation} and inspired by the \textit{do calculus} and \textit{twin networks} of \citet{Pearl_2009}, is a family of causal inference techniques that can be used to determine if a probability distribution $\prob[\nodes_{O}]$ is compatible or incompatible with a given causal structure $\graph$. As a preliminary summary, the Inflation Technique begins by \textit{augmenting} a causal structure with additional copies of its nodes, producing an \textit{inflated} causal structure, and then exposes how causal inference tasks on the inflated causal structure can be used to make inferences on the original causal structure. As a example, four inflations of the Triangle structure are depicted in \cref{fig:inflations}. Copies of nodes in the inflated causal structure are distinguished by an additional subscript called the \term{copy-index}. For example, node $A$ of \cref{fig:triangle_structure} has copies $A_1, A_2, A_3, A_4$ in the inflated causal structure in \cref{fig:the_web_inflation}. All such copies are deemed equivalent via a \term{copy-index equivalence} relation denoted `$\sim$'. A copy-index is effectively arbitrary, so we will refer to an arbitrary inflated copy of $A$ as $A'$.
    \[ A \sim A_1 \sim A' \not\sim B \sim B_1 \sim B' \]
    We preemptively generalize the notion of copy-index equivalence to other mathematical objects like sets, graphs, and groups by saying that $X \sim Y$ if and only if $X = Y$ upon removal of the copy-index. In addition to the common graph-theoretic terminology and notation presented in \cref{sec:causal_compatibility}, we define two more concepts necessary to formally define an inflation of $\graph$. First, an \term{induced subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is another graph composed of nodes $N$ and all edges $e$ of the original graph that are contained in $N$: $\Sub[\graph]{N} \defined \br{N, \bc{e = \bc{n \to m} \mid n, m \in N}}$. An \term{ancestral subgraph} of $\graph$ for a subset of nodes $N \subseteq \nodes$ is the induced subgraph due to the ancestry of $N$: $\AnSub[\graph]{N} \defined \Sub[\graph]{\An[\graph]{N}}$.
